This paper demonstrates that the stability of micronutrients in fortified foods depends on the interaction between processing conditions, the characteristics of the food matrix, and subsequent storage environments. Studies such as \citet{chepkoech}, \citet{noodle} or \citet{gari} demonstrate that pre- and post-fortification steps are closely linked. Being aware of this, basic research of \citet{li2coatsalt} and \citet{li3capsalt} contributed to a deeper understanding of the underlying mechanisms and consequently, studies from \citet{chepkoech} and \citet{sharma} contributed data on the different storage conditions. Studies such as \citet{li5cocoyam} or \citet{chepkoech} clearly demonstrate that temperature, humidity and light remain key factors that influence degradation, particularly for fat-soluble vitamins. Minerals were found to be generally more stable but still affected by the interplay between processing and storage conditions to a certain extent \autocite{saha}.
\par 
 At the same time, research by \citet{sharma}, \citet{li5cocoyam}, \citet{kumari} and \citet{saha} highlights that technological interventions, such as coating strategies, drying techniques, or the use of antioxidant protection systems, can substantially improve storage stability. These findings are particularly relevant because they demonstrate that micronutrient losses are not just unavoidable consequences of environmental conditions; rather, they can be actively reduced through appropriate technological methods.
\par  
Ultimately, the findings show that there are strong implications on interacting effects resulting in changes for micronutrient retention and indicate that fortification strategies are most effective when the choice of an appropriate fortification vehicle, processing steps, and the expected storage conditions are all put into consideration. 
\par 
In order to make fortification programs more reliable and cost-efficient and to combat hidden hunger effectively, there is still a need for further research that investigates complex interaction effects of micronutrients’ storage stability. 
