
%''Hidden hunger'' is a major health concern and is also known as “micronutrient deficiency”. It can be seen as a sort of undernutrition condition that results from consuming energy-dense foods but limited in vitamins and minerals. Micronutrient deficiencies are not restricted to economically poor countries; they also affect high-income regions such as Europe due to the changes in dietary patterns with increases in the consumption of processed foods \autocite{1ofori}. %ALT


\textit{Hidden hunger} is a major health concern and is also known as \textit{micronutrient deficiency}. It is a form of undernutrition resulting from the consumption of energy-dense diets that lack essential vitamins and minerals. Micronutrient deficiencies are not restricted to economically poor countries; they also affect high-income regions such as Europe due to changes in dietary patterns driven by the consumption of processed foods \autocite{1ofori}.
\par 
%\pp

The consequences of malnutrition and hidden hunger are severe. Annually, an estimated 1.1 million out of 3.1 million infant deaths are attributed to micronutrient deficiencies \autocites{2c}{largescale}. Less intense forms of malnutrition can cause minor issues like dizziness but can also lead to loss of vision if the malnutrition is advanced. The adverse effect of malnutrition and hidden hunger has forced several countries to address this worldwide problem. International movements, such as the “Scaling Up Nutrition Movement”, but also government programs, seek to fight malnutrition \autocites{4hidden}{5unnes}.
\par 
%\pp
There are four primary interventions that can be differentiated and are addressed to tackle malnutrition and hidden hunger: dietary diversification, food supplementation, food fortification and biofortification \autocites{6biofort}{7plants}. \par 
Food fortification involves adding specific nutrients to foods to enhance their nutritional value and help consumers meet the recommended daily allowance (RDA) for those nutrients \autocite{6biofort}. Particularly in developing countries, fortifying foods with nutrients such as iron, iodine and vitamins has greatly reduced the prevalence of diseases associated with nutrient deficiencies \autocite{8forti}. In Germany, for example, salt is iodized to prevent iodine-related disorders, including goiter \autocite{iodine}, and pregnant women are advised to increase their intake of folic acid in order to avoid anemia. These examples illustrate the diversity of fortification strategies and their potential public health impact. Hence, it is important to understand every aspect of micronutrient fortification, since the aforementioned problems can be highly individual and require deeper knowledge of the mechanisms that occur during food preparation as well as pre- and post-fortification. 
%
%
%
\par 
%\pp

Pre-fortification, also referred to as biofortification, increases the nutritional value of crops during their growth. This effect is achieved through various methods such as agronomic practices, conventional plant breeding or genetic engineering \autocite{1ofori}. Biofortification of Vitamin A in sweet potatoes or Golden Rice leads to higher values of Vitamin A in the finished products \autocite{1ofori}. Being performed only once, pre-fortification is a highly sustainable method of increasing nutritional value and thus can be viewed as a great long term solution. In contrast, during food preparation there are several mechanisms that hinder the complete preservation of micronutrients. For example, it has been shown that cooking fortified rice in excess water increases micronutrient loss, similiar to unfortified rice \autocite{10rice}.


%%#########################
%''Hidden hunger'' is a major health concern and results from micronutrient deficiences in food and does not affect only regions which are economically weak, but also appears to be a matter of concern in high-income continents like Europe. As for example, there is still a need for fortification in salt to combat iodine related health issues like enlargement of the thyroid gland \autocite{iodine}. Furthermore pregnant women are advised to ingest more folic acids, to avoid anemia. In Kenya, Vitamin A, B$_{9}$ (Folic acid) and B$_{12}$ are major concerns regarding micronutrient deficiences \autocite{chepkoech}. These forms of malnutrition can cause minor issues like dizziness but can also lead to loss of vision if the malnutrition is advanced. This small selection of examples illustrates its variety and its possible effect on almost every human. Hence, it is important to understand every aspect of micronutrient fortification since the mentioned problems can be very individual and require deeper knowledge about the mechanisms that occur during food preparation as well as pre- and post-fortification. 
%\par 
%How pre-fortification methods can enhance micronutrient retention has been shown in works such as blabla and bla. Food processing has great impact on micronutrient stability aswell, which is broadly examined. Study of blabla shows for example how blabla is influenced by bla. 
%#############################
\par 
%\pp
To our knowledge, studies on stabilizing micronutrients post-fortification receive less attention in literature than other aspects of fortification. Thus, food producers still rely on overage methods if they want to ensure sufficient amounts of micronutrients to combat hidden hunger. This approach is cost-increasing, hinders new ventures and should therefore be minimized, especially for economically weaker countries. This study aims to summarize recent findings on the topic, to provide greater clarity for food producers who need to ensure that their products contain minimum levels of nutrients in a cost-efficient manner.




%#############################
%While rice has been a staple food of interest in research about micronutrient retention, there is not such about flour to our knowledge. Since a broadening part of the population is eating baked goods like mandazis on a regular basis, this study aims to tackle this gap in research and to provide greater clarity for producers who need to ensure that their products contain minimum levels of nutrients.   \par 
%
%Awareness of the preservation of micronutrients in food over extended storage periods is playing an increasingly important role in food research. This ranges from food supply in war zones and areas affected by natural disasters to food supply in the aerospace sector. \par 

%This research paper examines the issue of potential micronutrient loss in fortified baked goods under tropical conditions. The aim is to provide greater clarity for producers who need to ensure that their products contain minimum levels of nutrients.   \par 
%#############################

% #################
% #################
% #################
% #################
% #################
% ################# ZU EINEM ANDEREN ZEITPUNKT ERWÄHNEN \par 

% #################
% #################
%It has already been established that pasta enriched with spinach and carrot powder generally retained sufficient levels of micronutrients even after 4 months \autocite{sharma}. However, data from this study also showed that, under tropical conditions, an overall loss of micronutrients of up to 40\% had been recorded. Another factor that should not be overlooked here is the packaging material, which, alongside temperature, has a significant impact. 

