Processing factors (solar vs. freeze-drying; steam-blanching vs. no pretreatment) significantly influenced both the initial micronutrient levels and the changes in mineral contents during storage of cocoyam leaves. However, the study demonstrated that process factor alone did not determine nutrient stability; rather, the interaction effects between drying, pretreatment, temperature, and time were more decisive. \par
In general, drying changed the matrix of cocoyam leaves from a water-rich, dilute structure into a solid-dense one. Consequently, freshly dried samples exhibited higher mineral concentrations than fresh leaves. When comparing solar and freeze drying, the two methods, each combined with steam blanching, showed differing effectiveness for individual minerals. The solar-dried, steam-blanched samples recorded the highest phosphorus content, whereas calcium levels were greatest in freeze-dried, unblanched samples.  \par
Similar effects were observed for steam blanching, which increased initial mineral content, especially of calcium and phosphorus. Yet, blanching also interacted with drying and temperature, meaning its benefits depended on the entire process chain rather than on the pretreatment step alone.
\par 
The underlying mechanism of the interdependent effect strength between certain factors is also discussed by \citet{gari}. In this study, the authors demonstrate that Red Palm Oil serves as the most efficient fortification vehicle, and combining it with toasted wheat bran as a stabilizing agent additionally supports the retention of Vitamin A. This is due to the naturally available antioxidants, which intercept radicals and hinder their interaction with the vitamin. As mentioned earlier, these kinetics are usually subject to the Arrhenius equation. However, in a food matrix there are also other factors - like the reduced density of the lipid environment - to consider. Considering this, there is a methodological limitation: although Red Palm Oil significantly improved retention under accelerated storage conditions, empirical data quantifying this protective effect under real-time ambient storage remains lacking. 
\par
More research on process factors was done by \citet{li2coatsalt}. They were collecting data on physical properties such as diameter, sphericity and coating thickness. Indicating that those influence the loss of micronutrients due to attrition of the coating. While this argumentation seems coherent, the extent of attrition-based losses of micronutrients has yet to be determined. 
\par
Research on coating effects was made by \citet{li3capsalt}. They demonstrated that applying a soy stearin coating to ferric pyrophosphate is highly effective in preventing reactions with fortified iodine, which would otherwise lead to iodine loss, as \citet{wegmueller} demonstrated, and further found that at higher temperatures this effect is decreasing. This shows again, that accelerated temperatures might contribute to a greater loss of micronutrients. 
