The mineral content in cocoyam leaves is substantially influenced by how processing and storage steps work together, rather than by a single factor. Interaction effects determine both the initial mineral levels and their evolution during storage, making postharvest handling a decisive factor in micronutrient retention. Storage conditions can either amplify or reduce nutrient losses depending on prior processing steps. Among the minerals studied, Phosphorus and calcium seemed to be the most sensitive, showing sharp declines over 42 days, while sodium remained largely unaffected by temperature and duration. \par
The observed moisture increase (from 7.5-7.8\% to 10-13\%) likely contributed to mineral dilution and structural changes within the dried matrix. Also warm storage (32 °C) consistently worsened calcium and phosphorus stability, reflecting enhanced chemical degradation and mineral redistribution in reactive mineral forms. The significant interaction between drying method and storage temperature demonstrates the importance of combinating initial drying techniques with appropriate storage protocols to preserve nutrient quality. 
 Overall, the findings suggest that appropriate combinations of drying, pretreatment, and controlled storage temperature are essential for micronutrient quality in dried leafy vegetables. In the broader context of fortified or processed foods, the study highlights that storage duration and temperature strongly affect mineral stability, particularly when combined with specific processing methods. Practically, processors should employ low-temperature drying, gentle pretreatments, and short-term storage under cool, dry conditions to preserve nutritional quality \autocite{li5cocoyam}. \par
These findings resemble those of \citet{chepkoech}, who observed similar temperature- and humidity-driven losses in vitamins within fortified maize flour. Both studies underline that cool, dry storage conditions are critical for maintaining micronutrient integrity.
To compare vitamin and mineral stability, it has been generally reported that vitamin losses are higher than mineral losses in fortified foods during storage \autocite{chepkoech}.


%The research of \citet{sharma} shows that there is less micronutrient retention with 


\citet{saha} reported results consistent with this general trend, showing significant degradation of vitamin A, whereas iron and zinc remained comparatively stable in extruded fortified rice stored under warm and humid conditions.
\par 
\citet{dutta} utilized a first-order kinetic model to quantify that the rate of carotenoid degradation of PVAC (0.01174) was almost three times higher than that of NPVAC (Non-Provitamin-A Carotenoids) (0.00381). This finding is consistent with research suggesting that vitamins are less stable compared to other  ingredients. Furthermore, biofortified maize hybrid APQH1 emerged as a promising model for high nutrient retention ($>$20\%).


