Process factors that are influencing the post fortification methods were mentioned by four studies. Findings are distinguished in two subcategories:
\begin{itemize}
\item Type of fortification substance applied and
\item Type of fortification method utilized
\end{itemize}
The findings also showed that the used vehicle and method can interact, therefore weaken or strengthen the initial effect. Some studies focus on both principles. 
Thus, these studies investigate not only a specific fortification vehicle but also the method with which the fortification is utilized. For instance, this is shown by \citet{noodle} with instant noodles that underwent a fortification process through addition of catfish powder with the pasta being tray dried or deep-fat fried. The combination of deep-fat frying with addition of catfish powder resulted in the highest values of cooking loss. This is attributed to the washing out of water-soluble micronutrients, which is more likely to occur through the formation of starch-lipid complexes during storage time \autocite{xueying}. Consequently, this shows that fortification vehicle and method are not seen as two separate processes but closely linked to each other.

\par

Rather than focusing on vehicle-method interactions, other studies have investigated isolated processing methods - specifically how modifying the physical delivery system can prevent nutrient degradation. One such method is applying a coating to fortification granules, an approach initiated by \citet{li2coatsalt} to ensure sufficient micronutrient retention. They did basic research and first steps to consider physical properties of fortification granules to ensure sufficient micronutrient retention. The recent findings indicate that properties such as coating thickness, size and shape have an impact on attrition. The authors indicate that attrition is contributing to resilience of micronutrients under harsh processing conditions. It is unclear if that might also contribute to post-fortification mechanisms. In this context, the findings of \citet{li3capsalt} provide valuable insights. The authors further investigated on the principles of physical properties. Their findings suggests that appling a soy stearin coating to ferric pyrophosphate is highly beneficial to prevent it from reacting with fortified iodine, which would result in iodine loss. Ferric pyrophosphate is more beneficial in terms of consumer acceptance and therefore an important fortification vehicle. The study showed that even under elevated temperature and humidity multifortified salt and double fortified salt remained stable after six months when soy stearin coating was applied. 
%%Also considering that among the multifortified salt the included zinc could also accelerate iodine loss which did not occur.
\par
Beyond the specific fortification method, the selection of an appropriate fortification vehicle also contributes significant to the storage stability. As shown in a study about the fortification of gari, which contributed to a better understanding of the importance of the right choice of a fortification vehicle. In \citeyear{gari}, \citeauthor{gari} aimed to find solutions for Vitamin A retention, since Vitamin A needs carefully choosen strategies in fortification practices considering its low stability \autocite{vitaproblems}. The authors aim to find a feasible approach on Vitamin A fortification in West Africa. With the result that Red Palm oil is the best fortification strategy to ensure high vitamin A retention in gari, a cassava-based West African food product when compared to retinyl palmitate or yellow cassava. Other studies have shown that Vitamin A fortification vehicles such as retinyl palmitate or $\beta$-carotene degrade rapidly under ambient conditions. Red Palm-oil presumably has more stability because of the presence of natural antioxidants as the authors state. In addition, cereal bran has been shown to be usable as a stabilising agent. These findings were observed under accelerated storage but literature suggests that these are applicable for ambient conditions as well. 

