This chapter consequently aims to support established principles, such as the Arrhenius equation, by collecting data from recent findings on temperature-time-regimes, humidity and sunlight exposure. \par 

\citet{chepkoech} assessed the impact of storage conditions on the retention of retinol and B-vitamins in selected commercial fortified maize flour. Maize flour, a widely consumed staple in developing countries, is commonly fortified with iron, zinc, retinol, and vitamins B$_1$, B$_2$, B$_3$, B$_6$, B$_9$, and B$_{12}$ to improve micronutrient intake. However, there are still many cases of micronutrient deficiencies, although fortification programs have been established. Temperature and relative humidity emerged as two major determinants of micronutrient stability in maize flour. Across all vitamins analyzed (retinol, thiamine, riboflavin, niacin, folate), higher temperature (35 °C) and higher relative humidity (83\% RH) consistently accelerated degradation, whereas samples stored at 25 °C / 75\% RH retained substantially more micronutrients over six‑months. This effect is likely due to an increase in oxidation rates and isomerization, especially for fat-soluble vitamins such as retinol. Although vitamin levels declined over six months, statistical analysis indicated that there is no significant interaction between storage time and condition for retinol, thiamine, niacin and folate, probably because the differences between the two storage environments (temperature/RH difference) were too small to be statistically significant. Riboflavin was the exception, showing a significant interaction likely explained by its high light sensitivity. Overall, the study showed a clear hierarchy of stability: Retinol and thiamine were the least stable, while niacin and folate remained comparatively stable. These findings indicate that even moderate increases in temperature and humidity accelerate oxidation and isomerization, confirming the Arrhenius principle that reaction rates rise exponentially with temperature.  \par

%%%%(Dutta et al. 2021)
Moreover, research from \citet{dutta} has demonstrated that the majority of PVAC (Provitamin-A Carotenoids) losses in biofortified maize hybrids occurred during the first three months of storage. These findings highlight the necessity of micronutrient stability immediately post-harvest and suggest that rapid intervention or reduced storage time is essential for nutritional preservation.
\par 
%%%%%Sahin et al. 
\citet{li4daylight} examined vitamin A (retinyl palmitate) retention in fortified sunflower oil over six months under varying light and packaging conditions. Light exposure was found to be the main driver of vitamin A loss and oxidation. Under daylight, especially in transparent bottles, vitamin A decreased dramatically, in some samples reaching zero after 6 months. In contrast, vitamin A remained relatively stable in brown, light-protective bottles regardless of light exposure. The decline correlated with increasing oil oxidation, likely due to interactions between oxidative lipid products and vitamin A. Optimal stability occurred when samples were stored in the dark, in brown/light-resistant packaging, and fortified with higher retinyl palmitate fortification levels (approximately 60-90 µg/g). Sunflower oil stored under daylight, particularly in pellucid bottles, tended to have the lowest oxidative stability and showed the greatest loss of retinyl palmitate. These findings are comparable to observations that humidity and heat accelerate micronutrient degradation in dry food matrices.
From a practical standpoint, sunflower oil should be kept away from direct light, stored for only a few months, and consumed promptly to minimize oxidative degradation and preserve vitamin A stability. \par 
 %%%%%Essilfie et al. AKA li5cocoyam
\citet{li5cocoyam} investigated mineral retention in cocoyam leaves, an underutilized yet nutrient-rich leafy vegetable, commonly consumed in Ghana. The leaves were treated by using different drying methods (solar drying and freeze drying), blanching pretreatment, two storage temperatures (room: 32 °C and refrigeration: 6.7 °C), and two storage durations (0 and 42 days). The results showed that mineral retention was mainly determined by interactions between processing and storage factors rather than by one single condition. Five different micronutrients - calcium, phosphorus, sodium, zinc and iron - displayed considerable differences in stability during storage. 
Calcium was highly unstable during storage, especially at 32 °C, showing major losses regardless of processing method, while sodium remained relatively stable and was mainly affected by processing. Storage temperature and storage duration did not significantly alter sodium content, indicating that sodium was the most temperature-stable mineral. Phosphorus was the most variable mineral, strongly influenced by combined effects of drying method, blanching, storage temperature, and time. Both phosphorus and calcium stability depended heavily on interactions between processing and storage factors rather than on any single factor alone. Zinc levels were very low (0,001-0,007 g/ 100 g) and mainly affected by interaction between processing and temperature conditions, with limited time-related effects, while iron levels were below the quantification limit. 
The study highlights that combined effects of drying method, pretreatment, and temperature determine mineral retention. This is again consistent with the Arrhenius‑based temperature‑time dependency.

 \par 
%%%%%Attaugwu
\citet{cookie} indicates that refrigerated storage is a more suitable storage condition than ambient storage. Among the micronutrients examined, vitamin E was the only one that remained relatively stable after 30 days, whereas vitamins B$_1$, B$_2$ and B$_3$ showed reduced retention, aligning with known mechanisms of micronutrient degradation.



%%%\par PASTA FUN WITH YOUR MUM \par 

In the study of \citet{sharma} pasta was enriched with spinach and carrot powder as well as millet flour. Retention rates of iron and vitamin A were monitored over a four-month storage period, measured monthly, under two temperature-humidity regimes:  25 °C/ 60\% RH and 40 °C/ 80\% RH. Two packaging materials were compared- polypropylene and aluminium laminates.
Pasta fortified with carrot powder and packaged in foil exhibited greater vitamin A retention than polypropylene. Vitamin A retention was significantly influenced by packaging type, light exposure, temperature, and storage duration,  whereas iron retention was affected primarily by storage time. The data further indicated that iron retention was highest in laminated packaging under ambient temperature conditions.
\par 
Similarly, \citet{saha} who summarized and compared findings on the storage stability of micronutrients in extruded fortified rice under varying environmental conditions, found that vitamin A losses increased exponentially with high temperature and humidity, whereas iron and zinc exhibited comparatively high stability. The study further demonstrated that besides temperature and humidity, the pH value can also play a decisive role in terms of micronutrient stability. Lowering the pH by adding ferrous sulfate or sodium ascorbate during dough preparation can reduce micronutrient losses due to oxidation, especially of iron.


