Food fortification methods are commonly divided into three chronological phases: pre-fortification, process-fortification, and post-fortification. Although this study concentrates on the post-fortification phase, a comprehensive understanding of the preceding stages is needed to contextualize the interdependent nature of micronutrient retention. \par
Pre-fortification refers to any intervention that occurs prior to industrial food processing. In practice, this primarily encompasses biofortification achieved through various methods such as agronomic practices, conventional plant breeding, or genetic engineering \autocite{1ofori}, effectively enhancing the nutritional baseline of the raw agricultural crop.  \par Process-fortification is understood as the deliberate addition of nutrients during food processing or directly to a ready-to-consume food vehicle. This stage is critically dependent on the strategic selection of both the food vehicle and the applied fortification method. It also includes altering the food matrix to facilitate the desired incorporation of the micronutrient, which ultimately plays a pivotal role in determining shelf-life stability. \par 

In contrast, the post-fortification phase concerns the retention and stability of the added micronutrients. This phase involves two groups of factors: 

\begin{enumerate}
\item Intrinsic factors that stem from the earlier phases. For example, the food matrix established during pre- or process-fortification strongly influences the ultimate stability of the nutrients.  Consequently, the present framework aims to integrate these structural dependencies to evaluate micronutrient losses under varying storage conditions.
\item Extrinsic, storage-related factors such as temperature, humidity, light exposure, time or packaging material. 
\end{enumerate}

\par 
\vspace*{2mm}
\begin{figure}[h]
\centering
\resizebox{.7\textwidth}{!}{
\begin{tikzpicture}[
    node distance=1.5cm,
    box/.style={rectangle, draw, minimum width=2.5cm, minimum height=1cm, align=center, thick},
    arrow/.style={-{Stealth}, thick}
]

    % Knoten
    \node[box,align=center] (post) {PRE-\\ \footnotesize FORTIFICATION};
    \node[box, right=of post,align=center] (during) {PROCESS-\\ \footnotesize FORTIFICATION};
    \node[box, right=of during,align=center] (pre) {POST-\\ \footnotesize FORTIFICATION};

    % Verbindungen
    \draw[arrow] (post) -- (during);
    \draw[arrow] (during) -- (pre);

    % Beschriftungen oben
    \node[above=0.3cm of post,align=center] (inc_f1) {\footnotesize action that increases \\ fortification};
    \draw[arrow] (inc_f1) -- (post);
    
    \node[above=0.3cm of during,align=center] (inc_f2) {\footnotesize action that increases \\ fortification};
    \draw[arrow] (inc_f2) -- (during);
    
    \node[above=0.3cm of pre,align=center] (inc_r) {\footnotesize action that increases \\ retention};
    \draw[arrow] (inc_r) -- (pre);

    % Beschriftung unten (Action & Curved Arrow)
    \node[below=0.8cm of post, font=\bfseries, align=center] (action) {action};
    \node[below=0.8cm of during, font=\bfseries, align=center] (action2) {action};
    \draw[arrow,dashed,  thick, scale=0.8] (action) -- (post);
    \draw[arrow,dashed, thick, scale=0.8] (action2) -- (during);
    
    \draw[-Latex,dashed, thick] ($(post.south)
    +(0.1,0)$).. controls ($(post.south) + (0,-2)$) and ($(pre.south) + (0,-2)$) .. ($(pre.south)+(0.2,0)$) 
        node[midway, below,align=center, scale=0.7] {increases \\ retention};
\draw[-Latex,dashed,thick] ($(during.south)
    +(0.1,0)$) .. controls ($(during.south) + (0,-1)$) and ($(pre.south) + (0,-1)$) .. (pre.south) 
        node[midway, above, align=center, scale=0.7] {increases \\ retention};
        
\end{tikzpicture}
}
\caption{Schematic representation of the various fortification-stages in chronological order, own representation}
\label{fortistages}
\end{figure}

\noindent 
The post-fortification method is governed by well-established physical principles. For instance, chemical processes may accelerate or decelerate under different temperature-time regimes, which can be predicted using the Arrhenius equation. This remains valid even when additional parameters, such as specific humidity conditions, are considered \autocite{arrhenius}. Since then, the scientific community has aimed to identify interactions between substances that are not yet described by existing formulas or empirically observed. Ultimately, findings that support established theoretical models remain highly valuable, as they provide essential data to refine our understanding of the underlying mechanisms.
The latter is shown, for instance, in meta reviews that identified ferric pyrophosphate as the most favorable compound for rice fortification, considering both micronutrient stability and consumer acceptance \autocite{10rice}. Moreover, emerging technologies can provide valuable insights into post-fortification mechanism. One such example is presented in a study by \citet{kumari}, which applied a coating strategy for rice involving microwave-assisted screw-conveying spraying. This method proved highly efficient because it had nearly the same retention properties compared to non-fortificated rice. 
